{\helveticaitalic{Supplementary Material}}

### 2022-03-30 tex/response.tex

\shortpoint{And fifth, the notation $n-n$ is non-ideal, as it looks like $n$ minus $n$. In my opinion, $n:n$ is more standard and clearer.}
\shortreply{Thank you for this suggestion, as it especially makes the $(n+1):(n+1)$ easier to read. As suggested, we have replaced the $n-n$ notation with $n:n$ everywhere in the revised manuscript.}

\subsection{Minor Comments}
\setcounter{point}{0}

\shortpoint{Line 31: It’s a CPG composed of reciprocally inhibitory neurons; referring to a ``reciprocally inhibitory CPG'' is misleading.}
\shortreply{Agreed. We changed ``reciprocally inhibitory CPG'' to ``CPGs composed of reciprocally inhibitory neurons'' in line \ref{line:A}.}

\shortpoint{The par. starting on line 38 is unclear: The $1-d$ conditions for $n:n$ solutions in [6] are stated to be for $n\leq 2$ (line 43); the authors should clarify if $n:n$ in line 48 also refers to $n \leq 2$ or not.}
\shortreply{Agreed. We added a clarification that the scalar conditions are valid only for $n\leq 2$ (line \ref{line:B}).}

\shortpoint{Results line 130: It is important to note that both neurons inhibit each other at all times. $s$ may get small but it's nonzero. Thus, ``inhibited'' cell is not really well-defined.}
\shortreply{Agreed. We changed ``inhibited cell'' to ``suppressed cell'', and added a short explanation, see \linerange{line:C1}{line:C2}.}

\shortpoint{Line 137: Wang \& Rinzel, 1992 (and perhaps Skinner et al. from 1993 or 1994) should be cited in reference to release.}
\shortreply{Added the \cite{wang1992} and \cite{skinner1994} references when ``release'' is mentioned in line \ref{line:D}.}

\shortpoint{I don’t understand Fig. 4B. The ISI is less than the IBI, so how can their ratio be bigger than 1? Or perhaps the axis label ``ISI/IBI'' does not refer to ISI divided by IBI? Clarification is needed.}
\shortreply{The $IBI$ notation was indeed unclear, and did not help in explaining our model assumptions, thank you for pointing this out. All mentions of $IBI$, as well as Fig. 4B (M0), have been removed from the revised manuscript. Instead, we provide a more straightforward numerical argument for the $ISI=T$ assumption in \linerange{line:E1}{line:E2}: For every stable $n:n$ solution in the period bifurcation diagram (\cref{fig:bif-diagram} in the revised manuscript), we compute all $ISI$s and find that they all fall within the interval $\left[376, 377\right]$ $\si{ms}$.}

\shortpoint{Line 200: “revolve” should be replaced by “evolve”.}
\shortreply{The whole paragraph formerly starting at line 194 (M0) has been rewritten.}

\shortpoint{Line 213 is incorrect: It’s not the decay of $d$ that matters but the decay of $s$ before the next spike occurs. Correction needed - except now I realize that lines 207-219 can be cut, as they add nothing relative to the previous paragraph.}
\shortreply{Definition of $g^{\star}$ was changed due to the change in equations, consequently the paragraph formerly starting in line 207 (M0) was removed.}

\begin{point}
\label{p:gstar}
It seems like the authors should be able to analytically compute or at least approximate $g^{\star}$ and should give some explanation for the delay in Fig. 6A, left branch. This must relate to the silent cell spending too short of a time in the silent phase. Fig. 4 is certainly relevant.\label{p:release-delay}
\end{point}
\shortreply{Thank you for this remark. Due to the aforementioned model changes and redefinition of $g^{\star}$ we can now express $g^{\star}$ explicitly in \cref{eq:gstar}.}

\shortpoint{Lines 246-7: The authors should revise because $s$ is determined by $d$ and by $\tau_{s}$.}
\shortreply{Agreed. In line \ref{line:E} we clarify that the value of $s$ ``at each spike time'' of the active cell depends only on $d$. This is because in the revised synapse model (eq. (\ref{eq:dot-s-up})) $s$ is set to the value $d$ when $v>v_{\theta}$.}

\shortpoint{Line 270: It seems like the active phase ends at time $(n-1)T+\Delta t$, yet the authors say it ends at $(n-1)T$. This may be more convenient for their analysis but it’s not correct usage of the phase terminology, so clarification is needed.}
\begin{reply}
It is indeed misleading when we let the active phase end at $(n-1)T$, since this time is the beginning of the last spike of the active cell.
The change of the model to \citet{bose2011} original equations, where $T=T_{a}+T_{s}$, and the according redefinition of the active phase hopefully clarifies this issue.
In the revised manuscript the active phase ends at $(n-1)T + T_{a}$, which is also the time when the previously active cell becomes silent.
\end{reply}

\shortpoint{It’s disorienting to see $\delta_n(d*)$ in eqn. (20) when just above (line 320) the same quantity is called $d_n = d(t_n^{-})$. The authors should pick one notation for both places.}
\shortreply{Agreed. We have removed the $d_{n}$ notation completely.}

\shortpoint{Cut line 339 and equation (27). These add a bit of confusion and nothing else.}
\shortreply{We believe that line 339 (M0) and eqn. (27) (M0) (\cref{eq:dn} in M1) are central to understanding the derivation of map $Q_{n}$. Eqn. (27) (M0) implies that if we know $\Delta t$, then we can predict the value of the depression variable of the active cell after $n$ spikes. This statement is not trivial because when computing $Q_{n}$ we have no knowledge of the initial $d^{\star}$. We have added some additional explanation in line \ref{line:abc} and would suggest to leave eqn. (27) (M0) as it is.}

\shortpoint{Fig. 9 caption: mention where the $Q_n$ curves intersect.}
\shortreply{Added intersection to caption in \cref{fig:FQ-maps}.}

\shortpoint{Eqn. (29): remind the reader that $\delta_n(d^{\star})$ comes from eqn. (20) and that $g^{\star}$ is obtained numerically.}
\shortreply{Added reminder in line \ref{line:remind}.}

\shortpoint{Lines 364-6 including eqn. (36) should be cut – they are neither new nor helpful here.}
\shortreply{Agreed. Lines have been removed as suggested.}

\shortpoint{Eqns. (37),(38) can and should be combined.}
\shortreply{Combined as suggested.}

\shortpoint{Eqn. (44) is confusing: here the authors want $d_f^\star = \phi_h(\bar{g})$, so it’s strange to express it as a function of $d_f^\star$ again.}
\shortreply{The $d_{f}^{\star}$ in eqn. (44) (M0) was a typo, thank you for pointing this out. It should be
  \begin{equation}
  \phi_{n}(\bar g) := G^{-1}(\bar g).
  \end{equation}
  Corrected accordingly in \cref{eq:phi}.
}

\shortpoint{Fig. 11B needs more explanation, such as a reminder that the orange curves are only computed over small intervals of $\bar{g}$ where the solution branch is stable.}
\shortreply{Agreed. Added reminder in the \cref{fig:final-bif} caption that the orange curves are computed from stable $n:n$ solutions that come from numerical integration of the system.}

\shortpoint{The notation $\bar{g}_{+}(n) < \bar{g}_{-}(n)$ seems strange – seems like these should be reversed (the math is fine, I’m questioning the choice of notation).}
\shortreply{We changed the $\bar{g}_{+}(n) < \bar{g}_{-}(n)$ notation to $\bar{g}_{\mathcal{L}}(n) < \bar{g}_{\mathcal{R}}(n)$, where the $\mathcal{L}$ and $\mathcal{R}$ subscripts stand for ``left'' and ``right'' branch borders.}

\shortpoint{Line 415: [21] is cited twice.}
\shortreply{Corrected.}

\shortpoint{Rather than stating eqn. (54), it would be clearer just to reference eqn. (47) there.}
\shortreply{Agreed. We removed eqn. (54) (M0) and referenced eqn. (47) (M0), see line \ref{line:bbb}.}

\shortpoint{A better explanation of what is shown in Fig. 12 is needed. Is this $\bar{g}_{+}(n)$ and $\bar{g}_{-}(n)$ for various n, computed numerically from (56) and (58)?}
\shortreply{Agreed. A short clarification was added in the text and captions to \cref{fig:final-bif}.}

\shortpoint{Discussion lines 459-462: Please explain what such “light” has been shed here. If none, as it appears, that’s OK for this math paper, but then this comment doesn’t really belong in the discussion.}
\shortreply{Agreed, our formulation was indeed misleading. This paper does not provide much insight on the underlying biological mechanisms in anti-phase burst generation. Instead, by ``underlying mechanisms'' we were referring to the ``mathematical principles'', e.g. importance of model parameters for the rhythm etc. A clarification was added in the text, line \ref{line:principle}.}

\shortpoint{I’m confused about lines 534-6. I have never heard of learning in a CPG. Please clarify what is meant.}
\shortreply{An elaborate explanation of learning in CPGs seems to be beyond the scope of this paper, and we have removed the learning reference. If the reviewer is interested the topic ``learning in CPGs'', please consider \citet{lukowiak1999}, where the authors experimentally study learning through operant conditioning in the respiratory CPG of the Lymnaea stagnalis snail, which consists of three inter-neurons. Interestingly, they show that in this CPG learning seems to occurs on both the synaptic level (change in connection strength), and cell-intrinsic level (changes in membrane properties).}

% % Begin a new reviewer section
% \reviewersection

% \begin{point}
% 	This is the first point of Reviewer \thereviewer. With some more words foo
% 	bar foo bar ...
% \end{point}

% \begin{reply}
% 	Our reply to it with reference to one of our points above using the \LaTeX's
% 	label/ref system (see also \ref{pt:foo}).
% \end{reply}

\section{Reviewer 2}
\label{sec:r2}
\subsection{Major Comments}
\textbf{Note on terminology and notation for reviewer 2:} In our replies to reviewer 2 we used the same terminology as used in the original manuscript. This is because the majority of the terminology changes were suggested by reviewer 1. In the following replies we wanted to focus on the content of the points raised by reviewer 2, instead of burdening them with new terminology.
\setcounter{point}{0}

\begin{point}
My major concern is about a few inaccuracies in the terminology.
The authors several times repeat that $n - n$ solution ``bifurcates'' to $(n + 1) - (n + 1)$ one (page 3, line 78; page 8, line 281; page 11, line 346; page 14, lines 3-4 of Sec. 3.6; page 14, line 423).
I cannot fully agree with such a formulation, since (as follows, e. g., from Eqs. (51) and (52)) there are ranges of the bifurcation parameter (coupling strength) $\bar g$ where two subsequent solutions coexist.
When one says that solution A ``bifurcates'' to solution B, it usually means that before the bifurcation only solution A exists and after the bifurcation only solution B exists, which is not the current case.
The authors should revise this point to avoid confusion.
\end{point}

\begin{reply}
We agree with the reviewer's formulation of ``bifurcation'', i.e. before the bifurcation point only solution A exists and after only solution B, and that bistability between $n-n$ and $(n+1)-(n+1)$ solutions should not be referred to as ``bifurcation''.
However, doesn't the loss of stability at the left and right branch borders qualify for the reviewer's definition of bifurcation?
That is, near the right border $\bar g_{-}(n)$ of a $n-n$ branch, as $\bar g$ is increased beyond $\bar g_{-}(n)$ the $n-n$ solution ``bifurcates'' into a $(n+1)-(n+1)$ solution when the $n-n$ solution loses stability (similarly near the left branch border as $\bar g$ is decreased).
This use of the term ``bifurcates'' is consistent with \cite{bose2011}, e.g. see p. 48: ``\dots, we will analytically explain why the bifurcation from a $n-n$ solution occurs at periods of $2nT$'' or p. 49: ``Further, the condition also implies that a $1-1$ solution bifurcates to another solution when \dots''.
The lines in the original manuscript that were pointed out by the reviewer use the term ``bifurcates'' to refer to these branch borders.
Unless we are misunderstanding the reviewer, we would suggest to leave these lines unchanged.
However, we are open for an alternative terminology that more accurately describes what is happening at the branch borders.
\end{reply}

\begin{point}
By the same reason, I suggest the authors to avoid the term ``period increment bifurcation'' (page 1, line 15; page 2, line 69; page 14, lines 408, 413, 416 and 419; page 17, lines 509 and 516), and moreover, such term does not exist.
The confusion could have been appeared because of the title of Ref.[23].
The authors of that reference meant a particular type of the big bang bifurcation, where the latter is a codim-2 bifurcation, an organizing center.
On the other hand, one can refer to the period increment bifurcation structure (or scenario), which consists of the parameter regions corresponding to periodic dynamics (periodicity regions) that are organized in the parameter space according to a particular principle.
However, the bifurcations defining the boundaries of these periodicity regions may be different.
For instance, in works by Avrutin et al. the boundaries of such regions were associated with boundary collision bifurcations, since the map there considered was discontinuous.
In the current work, it is not clear which bifurcation is responsible for appearance/disappearance of the $n-n$ solution.
It is not a trivial question and certainly requires deeper analysis, but it is incorrect to call it ``period increment bifurcation''.
\end{point}
\begin{reply}
This comment is very helpful, thank you.
The reviewer is correct, the term ``period increment bifurcation'' does not exist, Avrutin and colleagues indeed only use the terms ``period increment scenario'' or ``structure''.
Throughout the revised manuscript we have replaced the term ``period increment bifurcation'' by one of the  following: ``period increment scenario'', ``period increment dynamics'', or simply ``bifurcation''.
The changed lines in the revised manuscript are: line \ref{line:abstract}, line \ref{line:branchA}, line \ref{line:branchB}, and \linerange{line:disc-pincA}{line:disc-pincB}.
The \cref{sec:borders} title was changed to ``Stable solution branch borders''.
\end{reply}

\subsection{Minor Comments}
\setcounter{point}{0}

\shortpoint{Page 2, line 36: change “explaination” to “explanation”.}
\shortreply{Corrected.}

\shortpoint{Page 5, line 158: insert “as” between “well” and “irregular”.}
\shortreply{Corrected.}

\shortpoint{Page 5, line 158: It is claimed that in the certain range of the parameter $\bar g$ (marked in fig. 4A), there exist non-symmetric $n-m$ and even irregular solutions. Non-symmetric solutions are mentioned once more in Sec. 4 in connection with an asymmetric coupling. Can such solutions indeed appear in the symmetric version of the system? If yes, could the authors provide an example? Or alternatively, the respective sentence in line 158 can be developed a bit concerning this point.}

\begin{figure}[h!]
\centering
\includegraphics[width=0.7\textwidth]{irregular}
\caption{Voltage traces of an ``irregular'' solution with $\bar g=0.581$ $(\si{mS/cm^{2}})$. \label{fig:irregular}}
\end{figure}

\begin{reply}
\Cref{fig:irregular} shows an example of the aforementioned ``irregular'' solutions.
The figure was produced with strong symmetric coupling $\bar g=0.581$ $(\si{mS/cm^{2}})$, which is close to the $\bar g_{s}$ associated with the left border of the branch of suppressed solutions.
An integration time step of $dt=0.5$ $\si{ms}$ was used.
To get rid of transients the system was integrated for $500,000$ $\si{ms}$, and \cref{fig:irregular} shows the last $20,000$ $\si{ms}$.
It would be interesting to explore how chaotic the system is for large $\bar g$, but this would likely distract from the main story of the paper, which is also the main reason why we have not included this graph in the paper.
\end{reply}

\shortpoint{Page 6, line 183: The authors probably meant “fig. 4B” instead of “fig. 4A”, as the latter does not show ISI (only for the suppressed solution when it is equal to the period).}
\shortreply{Fig. 4 (M0) was removed from the paper.}

\shortpoint{Page 7, line 235: Did the authors mean ``$\bar g s$ crosses $g^{\star}$''?}
\shortreply{Corrected.}

\shortpoint{Page 7, line 246: It should be “$g^\star$” instead of “$g^*$” like throughout the manuscript.}
\shortreply{Corrected.}

\shortpoint{Page 12, line 371: It should be “is not trivial”.}
\shortreply{Corrected.}

\shortpoint{In Eq. (44) the function $G^{-1}_{n}$ cannot depend on $d^{\star}$, please revise.}
\shortreply{Indeed, thank you for spotting this. $G^{-1}_{n}$ depends on $\bar g$. Changed accordingly.}

\shortpoint{Page 13, line 383: Please remove the word “we”.}
\shortreply{Corrected.}

\shortpoint{Page 14, line 415: Ref. [21] is written twice.}
\shortreply{Corrected.}

\shortpoint{Page 17, line 511: In “Avrutin et al. and colleagues” either “et al.” or “and colleagues” should be removed.}
\shortreply{Corrected.}

\shortpoint{Fig. 1A: Marking the threshold $v_{\theta}$ would be helpful.}
\shortreply{Added $v_{\theta}$ indicators. to \cref{fig:nullclines}.}

\shortpoint{Fig. 4: The regions of overlapping (bistability) are obviously distinguishable. However, it would be helpful if they are highlighted, for instance, by vertical lines or colored vertical stripes, so that one can easier guess the approximate critical values of $\bar g$.}
\shortreply{Good idea. This will be done in the next iteration of the review process (if there is one).}

\shortpoint{Caption of Fig.10: It should be $\Pi_{n}: d^{\star}\mapsto d^{\star}$.}
\shortreply{Corrected.}

\bibliographystyle{apalike} % for Health, Physics and Mathematics articles
\bibliography{bibliography.bib}
